The pollination trade-off

### 2018-08-26 paper/manuscript.Rmd
FIgure coefficient averages includes relative variable importance

@@

```{r fig-model-results-global, fig.height = 1.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Results are shown for models with explanatory var"}
drake::readd(fig_coefficient_averages)
```

>>>>

```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Results are shown for models with explanatory var"}
drake::readd(fig_coefficient_averages)
```

@@
